### 2013-10-07 Paper/main.tex
Created the paper folder

%\title{SWEETcam submission for IEEE Computer}

%%
%% Draft version 1.0
%%
%% Authors:
%% Kevin Abas
%% Caio Porto
%% Katia Obraczka 
%%

%% The template used was by Michael Shell
%% see http://www.michaelshell.org/
%% for current contact information.

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE! 
%% User assumes all risk.
%% In no event shall IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.

%%*************************************************************************

\documentclass[journal,transmag]{IEEEtran}

% *** GRAPHICS RELATED PACKAGES ***
%
\usepackage{graphicx}
\ifCLASSINFOpdf

\else

\fi

% *** ALIGNMENT PACKAGES ***
%
\usepackage{array}

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/url/
% Basically, \url{my_url_here}.

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
% Do not put math or special symbols in the title.
\title{Removing Physical Limits, \textsc{Secuirity cameras of the Future}}

% author names and affiliations
% transmag papers use the long conference author name format.

\author{\IEEEauthorblockN{Kevin Abas\IEEEauthorrefmark{1},
Caio Porto\IEEEauthorrefmark{2},
Katia Obraczka\IEEEauthorrefmark{1}}
\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Engineering,
University of California Santa Cruz, CA 95064 USA}
\IEEEauthorblockA{\IEEEauthorrefmark{2}Escola Politecnica ´
Avenida Athos da Silveira Ramos ´
Rio de Janeiro, 21941-909, Brazil}
}

% for Transactions on Magnetics papers, we must declare the abstract and
% index terms PRIOR to the title within the \IEEEtitleabstractindextext
% IEEEtran command as these need to go into the title area created by
% \maketitle.
% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\IEEEtitleabstractindextext{%
\begin{abstract}
The abstract goes here.
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
IEEEtran, journal, \LaTeX, magnetics, paper, template.
\end{IEEEkeywords}}

% make the title area
\maketitle

\IEEEdisplaynontitleabstractindextext

\IEEEpeerreviewmaketitle

\section{Introduction}

% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
\IEEEPARstart{T}{his} paper discusses ...

\subsection{Background, motivation} 
\-- Goals of the paper, What problems this papers solves \\

% needed in second column of first page if using \IEEEpubid
%\IEEEpubidadjcol

\subsubsection{Today's applications (summary)}
\-- Some things current Smart Camera networks assist with when it comes to 
surveillance and crime detection nodes. \\

\section{Requirements for today's wireless Smart Camera Networks}
\-- What are some more recent technologies being used and discovered by
researchers today. \\

\section{Wireless Smart Camera Networks Taxonomy}
\-- Purpose criteria for classification of wireless Smart camera networks \\ \\
\-- A comparison chart of different hardware components of their systems 
	being used\\ \\
\-- A comparison chart of software design features (computer vision, network
	topologies, bandwidth/energy saving techniques, etc. )\\ \\
\-- Explain each classification criterion, provide examples, etc.\\ \\

\section{Example Wireless Smart Camera Systems}
\-- Going into more detail of possibly one of the examples shown above in
	the taxonomy\\ \\
\--

\section{Our Project}

\subsection{Hardware}
 \-- Discuss breifly about the different components and why they were chosen \\

\subsubsection{WiFi 802.11n \\}
\subsubsection{MSP430 \\}

% needed in second column of first page if using \IEEEpubid
%\IEEEpubidadjcol

\subsection{Software}
\subsubsection{Image Processing}
\- Considering the constraints of the system in terms of price and hardware, it is used techniques of background subtraction to do the object detection. When started, the program keep taking pictures and process them using Mixture of Gaussian (MoG) method by Stauffer and Grimson. With the foreground in hands we find the contours and then a bounded box is applied following the contours' limit. To remove some noise and false detection a step is added to ignore objects of small size. The object classification is the most processor consumption  processes for most of the pedestrian detection systems, because it is used training techniques to classify the objects based on a previous stored database. In our case, to reduce the process we classify the objects by looking at their dimensions, they are classified as human if the height is two times bigger than the width we classify as a person. \\
\begin{figure}[h!]
\centering
\includegraphics[scale=0.3]{imageprocessing}
\end{figure}	
\- This light system can generate some false alarms, but in association with the whole system, and its sensors, it can be improved for a better performance. There are other more robust object detection methods that could be used, but we would have a very low fps rate. \\
\- We developed using the Raspberry Pi camera module, which has already an API in C language and capable of capturing 1920x1080 resolution color images with 30 fps rate. For the image processing, we chose the Open Source Computer Vision Library (OpenCv). Our computer vision system is developed in C++ for better integration between the OpenCV and the API.\\

\subsection{Future Goals}

\section{Future Directions for Smart Wireless Camera Networks}
\-- Discuss research that has been proposed in the area and that is just begining to be implemented or hasn't yet at all.\\

\section{Conclusion}
\-- tie up paper

% use section* for acknowledgement
\section*{Acknowledgment}

\-- might not need this ...

% Can use something like this to put references on a page
% by themselves when using endfloat and the captionsoff option.
\ifCLASSOPTIONcaptionsoff
  \newpage
\fi

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{1}

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\end{thebibliography}

% if you will not have a photo at all:
\begin{IEEEbiographynophoto}{Kevin Abas}
Biography text here.
\end{IEEEbiographynophoto}

\begin{IEEEbiographynophoto}{Caio Porto}
Biography text here.
\end{IEEEbiographynophoto}

\end{document}

% *** MATH PACKAGES ***
%
%\usepackage[cmex10]{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics. If using
% it, be sure to load this package with the cmex10 option to ensure that
% only type 1 fonts will utilized at all point sizes. Without this option,
% it is possible that some math symbols, particularly those within
% footnotes, will be rendered in bitmap form which will result in a
% document that can not be IEEE Xplore compliant!
%
% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation Results.}
%\label{fig_sim}
%\end{figure}

% Note that IEEE typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command,
% and the \label for the overall figure must come after \caption.
% \hfil is used as a separator to get equal spacing.
% Watch out that the combined width of all the subfigures on a 
% line do not exceed the text width or a line break will occur.
%
%\begin{figure*}[!t]
%\centering
%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
%\label{fig_second_case}}
%\caption{Simulation results.}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat[]), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.

% An example of a floating table. Note that, for IEEE style tables, the 
% \caption command should come BEFORE the table. Table text will default to
% \footnotesize as IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
%\begin{table}[!t]
%% increase table row spacing, adjust to taste
%\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
%\caption{An Example of a Table}
%\label{table_example}
%\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
%\begin{tabular}{|c||c|}
%\hline
%One & Two\\
%\hline
%Three & Four\\
%\hline
%\end{tabular}
%\end{table}

% Note that IEEE does not put floats in the very first column - or typically
% anywhere on the first page for that matter. Also, in-text middle ("here")
% positioning is not used. Most IEEE journals use top floats exclusively.
% Note that, LaTeX2e, unlike IEEE journals, places footnotes above bottom
% floats. This can be corrected via the \fnbelowfloat command of the
% stfloats package.

% if have a single appendix:
%\appendix[Proof of the Zonklar Equations]
% or
%\appendix  % for no appendix heading
% do not use \section anymore after \appendix, only \section*
% is possibly needed

% use appendices with more than one appendix
% then use \section to start each appendix
% you must declare a \section before using any
% \subsection or using \label (\appendices by itself
% starts a section numbered zero.)
%

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

### 2013-10-16 Paper/main.tex
starting taxonomy

@@
 
+% ** BIBTEXT PACKAGE **
+\usepackage{cite}
+
+%%----------------------------------------------------------------------
+
 \begin{document}
-%
-% paper title
-% can use linebreaks \\ within to get better formatting as desired
-% Do not put math or special symbols in the title.
-\title{Removing Physical Limits, \textsc{Secuirity cameras of the Future}}
 
-% author names and affiliations
-% transmag papers use the long conference author name format.
+%% ***********************  THE TITLE **********************************
+
+\title{Designing Efficient Smart Camera Networks For Public Saftey}
+
+%% ***********************  AUTHORS ************************************
 
@@
 
-% for Transactions on Magnetics papers, we must declare the abstract and
-% index terms PRIOR to the title within the \IEEEtitleabstractindextext
-% IEEEtran command as these need to go into the title area created by
-% \maketitle.
-% As a general rule, do not put math, special symbols or citations
-% in the abstract or keywords.
+%% ***********************  AUTHORS ************************************
+
 \IEEEtitleabstractindextext{%
@@
 
-% Note that keywords are not normally used for peerreview papers.
+%% ********************** IEEE KEYWORDS ********************************
+
 \begin{IEEEkeywords}
@@
 
-% make the title area
+%% Title Configurations (From Template)
 \maketitle
+\IEEEdisplaynontitleabstractindextext
+\IEEEpeerreviewmaketitle
 
-\IEEEdisplaynontitleabstractindextext
-
-\IEEEpeerreviewmaketitle
+%% *********************  BEGIN PAPER **********************************
 
@@
 
-% Here we have the typical use of a "T" for an initial drop letter
-% and "HIS" in caps to complete the first word.
 \IEEEPARstart{T}{his} paper discusses ...
@@
 
-% needed in second column of first page if using \IEEEpubid
-%\IEEEpubidadjcol
-
 \subsubsection{Today's applications (summary)}
@@
 
-\section{Requirements for today's wireless Smart Camera Networks}
-\-- What are some more recent technologies being used and discovered by
-researchers today. \\
+%%Requirements for today's wireless Smart Camera Networks
+\section{Smart Camera Surveillance}
+Researchers and Commercial companies are designing wireless smart camera networks in surveillance applications to prevent crimes in public spaces. To
+understand how these state of the art systems are improving on designs of the past one must define what makes these surveillance systems "smart". These
+smart camera network systems have common goals when it comes creating more efficient surveillance applications. First, the issue of network resource
+utilization is an issue all systems need to consider if those surveillance systems are to be scalable in crowded wireless deployment scenarios. Then in
+almost every application considering power consumption of each node is very important if one is give an analysis of the systems efficiency. If these
+systems are to be monitoring public spaces the smart camera networks need to be keeping the data recorded secure and also ensuring that the data recorded
+is actually quality information that could be used by officials. \\
 
@@
 
-% needed in second column of first page if using \IEEEpubid
-%\IEEEpubidadjcol
-
 \subsection{Software}
@@
 \centering
-\includegraphics[scale=0.3]{imageprocessing}
+\includegraphics[scale=0.3]{imageprocessing.jpg}
 \end{figure}	
@@
 \-- tie up paper
+~\cite{DSPcam}
+~\cite{HuSIMS}
+~\cite{Citric}
+~\cite{OmniEye}
+~\cite{ScoutNode}
+~\cite{SensEye}
+~\cite{WiFLIP}
 
-% use section* for acknowledgement
-\section*{Acknowledgment}
-
-\-- might not need this ...
+%% *************************  END PAPER **********************************
 
@@
 % by themselves when using endfloat and the captionsoff option.
-\ifCLASSOPTIONcaptionsoff
-  \newpage
-\fi
+%\ifCLASSOPTIONcaptionsoff
+%  \newpage
+%\fi
 
-% references section
+%% ******************  REFERENCE SECTION **********************************
 
-% can use a bibliography generated by BibTeX as a .bbl file
-% BibTeX documentation can be easily obtained at:
-% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
-% The IEEEtran BibTeX style support page is at:
-% http://www.michaelshell.org/tex/ieeetran/bibtex/
-%\bibliographystyle{IEEEtran}
-% argument is your BibTeX string definitions and bibliography database(s)
-%\bibliography{IEEEabrv,../bib/paper}
-%
-% <OR> manually copy in the resultant .bbl file
-% set second argument of \begin to the number of references
-% (used to reserve space for the reference number labels box)
-\begin{thebibliography}{1}
+\bibliography{Bib.bib}{}
+\bibliographystyle{plain}
 
-\bibitem{IEEEhowto:kopka}
-H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
+%% ******************  AUTHOR BIOGRAPHIES *********************************
 
-\end{thebibliography}
-
-% if you will not have a photo at all:
 \begin{IEEEbiographynophoto}{Kevin Abas}
@@
 \end{document}
+
+%%------------------------------------------------------------------------
 
@@
 %
-
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-%\IEEEtriggeratref{8}
-% The "triggered" command can be changed if desired:
-%\IEEEtriggercmd{\enlargethispage{-5in}}

### 2013-10-16 Paper/main.tex
added bandwidth section

@@
 %%Requirements for today's wireless Smart Camera Networks
+
 \section{Smart Camera Surveillance}
@@
 
-\section{Wireless Smart Camera Networks Taxonomy}
-\-- Purpose criteria for classification of wireless Smart camera networks \\ \\
+%% Wireless Smart Camera Networks Taxonomy Divided into 3 sections
+%% 1 Bandwidth efficieny 2 power consumption 3 Quality of data
+\subsection{Bandwidth Efficiency}
+Video data is rich with useful information that other sensor source can’t provide, however video data quickly becomes very large in size as time goes on.
+Nodes competing for network connectivity while maintaining quality on live video feed can soon become a problem as the network grows or if other nodes
+not in the system share the connection. One way to combat this is by assuring the data recorded is useful and actually recording video data that can be
+used to do detection of events. A common technique is to use other non-image sensors to provide separate data that can be used to determine if the camera
+should record video at all.
+
 \-- A comparison chart of different hardware components of their systems 
@@
 \-- Explain each classification criterion, provide examples, etc.\\ \\
+
+\subsection{Lowering Power Consumption}
+
+\subsection{Quality of data produced}
 
@@
 
-\section{Conclusion}
-\-- tie up paper
+\section{Lessons to take away}
+
+\-- just so it compiles here are the references to be used:
 ~\cite{DSPcam}

### 2013-10-16 Paper/main.tex
added CV section and new refs

@@
 \begin{IEEEkeywords}
-IEEEtran, journal, \LaTeX, magnetics, paper, template.
+Wireless Sensor Networks, Smart Camera Networks, Surveillance, Computer vision.
 \end{IEEEkeywords}}
@@
 
-\IEEEPARstart{T}{his} paper discusses ...
+\IEEEPARstart{T}{his} paper discusses an overview of how Smart Camera Networks have
+influenced todays surveillance systems.
 
@@
 Researchers and Commercial companies are designing wireless smart camera networks in surveillance applications to prevent crimes in public spaces. To
-understand how these state of the art systems are improving on designs of the past one must define what makes these surveillance systems "smart". These
-smart camera network systems have common goals when it comes creating more efficient surveillance applications. First, the issue of network resource
-utilization is an issue all systems need to consider if those surveillance systems are to be scalable in crowded wireless deployment scenarios. Then in
-almost every application considering power consumption of each node is very important if one is give an analysis of the systems efficiency. If these
-systems are to be monitoring public spaces the smart camera networks need to be keeping the data recorded secure and also ensuring that the data recorded
-is actually quality information that could be used by officials. \\
+understand how these state of the art systems are improving on designs of the past, one must define what makes these surveillance systems "smart". 
+These smart camera network systems have common goals when it comes creating more efficient surveillance applications. First, the issue of network
+resource utilization is an issue all systems need to consider if those surveillance systems are to be scalable in crowded wireless deployment 
+scenarios. Then in almost every application considering power consumption of each node is very important if one is give an analysis of the systems 
+efficiency. If these systems are to be monitoring public spaces the smart camera networks need to be keeping the data recorded secure and also ensuring 
+that the data recorded is actually quality information that could be used by officials. \\
 
@@
 
+\subsection{Lowering Power Consumption}
+When discussing wireless sensor networks , power consumption is always brought up as a concern
+
+\-- Use comparision chart in survey paper to show power consumption comparisons of current smart camera platforms\\ \\
+
+\subsection{Quality of data recorded}
+
+\section{Processing the Video Data}
+
+By the computer vision side, we can see that the background subtraction is the most used method to detect moving objects with single cameras in a 
+real-time world. There are different algorithms to implement it, with different computer efficiencies and accuracies, what can make each one more
+suitable for each system. Methods like Mixture of Gaussians (MoG) or simple frame differencing are largely used, but the problem with these methods is
+their computational efficiency. In ~\cite{CS-MoG} it is shown the possibility of having a low power and computationally efficient (up to 5 times
+faster) system based on background subtraction using a known method: Compressed Sensing. Using CS is possible to compress the image, in other words,
+reduce the amount of data to be processed, while retaining much of the original image. The compressed image can be submitted to a MoG algorithm to
+detect the objects on the scene with a lower solution complexity. The results shown a very efficient system, that they called CS-MoG, with an accuracy
+very close to a system that uses MoG only.
+
+The Citric system one that resembles ~\cite{CS-MoG} by the steps that are used in the object detection.
+At first they make a comparison of computational efficiency relative to the complexity of compressing and uncompressing using JPEG and Compressed Sensing, resulting in a better performance of the CS  for uncompressing.
+After that they use frame differencing to do background subtraction and then track the objects and store their tracks.
+On the HuSIMS system they take one step further after tracking the objects, it is implemented an algorithm that is able to trigger alarms if something looks irregular.
+After doing the object tracking they are able to define regions, representing where the most common tracks pass by, and sinks, representing places where the objects usually appear or disappear from the scene.
+Having these two defined sections there is an algorithm capable of analyzing the image and verify, for example, if the objects of a certain type is following the expected region for its type, or if the object went from one sink to another.
+In a case where one of these predicted behaviors looks different, an alarm is triggered notifying that a problem could happened.
+A problem very common with single camera systems is the object occlusions that can occurs when an object cross by other moving or static objects.
+A good method for this case is shown in ~\cite{Occlusion}.
+After a background subtraction using the Approximate Median Filter to detect the objects, they are classified accordingly to the change of their shape through the time.
+It is used a Kalman filter to predict the position of the objects and then compare the current positions with the predicted ones through an algorithm that allows the system to classify the object as a single person or a group of people.
+The particular characteristic of this algorithm is the ability to track objects with complete occlusion for a long duration.
+Different implementations for security camera networks are emerging, each one with its characteristics, performance and advantages.
+By looking at all the implementations already said, we can say that a good system could be made by the union of all these methods, if performances wasn’t a constraint, because in most of them it is used the same base algorithm but with different securities and tracking objectives.
+Create an efficient system could mean a hybrid one.
+
+\section{Example Wireless Smart Camera Systems}
+
+\-- A comparison chart of software design features (computer vision, network
+	topologies, bandwidth/energy saving techniques, etc. )\\ \\
+\-- Going into more detail of possibly one of the examples shown above in
+	the taxonomy\\ \\
 \-- A comparison chart of different hardware components of their systems 
 	being used\\ \\
-\-- A comparison chart of software design features (computer vision, network
-	topologies, bandwidth/energy saving techniques, etc. )\\ \\
-\-- Explain each classification criterion, provide examples, etc.\\ \\
-
-\subsection{Lowering Power Consumption}
-
-\subsection{Quality of data produced}
-
-\section{Example Wireless Smart Camera Systems}
-\-- Going into more detail of possibly one of the examples shown above in
-	the taxonomy\\ \\
-\--
+\-- A discussion of both research and commercial designs\\ \\
 
@@
 
-\subsubsection{WiFi 802.11n \\}
-\subsubsection{MSP430 \\}
+\subsubsection{Why we chose Wifi \\}
+\subsubsection{Multimodal capabilities \\}
 

### 2013-10-29 Paper/main.tex
Finished sections 2 & 3

@@
 %%
-%% Draft version 1.0
+%% Draft version 2.0
 %%
@@
 %%
-
-%% The template used was by Michael Shell
-%% see http://www.michaelshell.org/
-%% for current contact information.
 
@@
 
+% ** CAPTION PACKAGE **
+\usepackage{caption}
 %%----------------------------------------------------------------------
@@
 
-\title{Designing Efficient Smart Camera Networks For Public Saftey}
+\title{Efficient Smart Camera Networks For Public Safety}
 
@@
 \begin{abstract}
-The abstract goes here.
+\textit{Abstract} \-- With the advancement of wireless smart camera platforms many systems have emerged offering more 
+efficient surveillance solutions for public spaces. After surveying more recent surveillance systems from the research community
+a classification is created to better help us understand what the future holds in this field.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-Wireless Sensor Networks, Smart Camera Networks, Surveillance, Computer vision.
+Wireless sensor networks, Smart camera networks, Computer vision, Sensor networks, Human safety
 \end{IEEEkeywords}}
@@
 
-\IEEEPARstart{T}{his} paper discusses an overview of how Smart Camera Networks have
-influenced todays surveillance systems.
-
-\subsection{Background, motivation} 
-\-- Goals of the paper, What problems this papers solves \\
-
-\subsubsection{Today's applications (summary)}
+\IEEEPARstart{T}{his} paper discusses an overview of how Smart Camera Networks are changing surveillance systems of today.\\
+\-- Goals of the paper, What problems this papers solves, background, motivation \\
+\-- discuss Wireless sensor networks in general and how data rich video sensor are\\
 \-- Some things current Smart Camera networks assist with when it comes to 
@@
 
-\section{Smart Camera Surveillance}
-Researchers and Commercial companies are designing wireless smart camera networks in surveillance applications to prevent crimes in public spaces. To
-understand how these state of the art systems are improving on designs of the past, one must define what makes these surveillance systems "smart". 
-These smart camera network systems have common goals when it comes creating more efficient surveillance applications. First, the issue of network
-resource utilization is an issue all systems need to consider if those surveillance systems are to be scalable in crowded wireless deployment 
+\section{Wireless Smart Camera Surveillance}
+Researchers and Commercial companies are designing wireless smart camera networks in surveillance applications to prevent crimes, detect environmental emergencies,
+monitor behavior of the elderly, and track vehicular traffic in public spaces. Many camera platforms have been designed to meet strict hardware requirements
+~\cite{Flexi-WVSNP} for wireless deployment in surveillance systems. However, different requirements must be stated when looking at the application specific 
+scenario of surveillance in public spaces. To understand how these state of the art systems are improving on designs of the past, one must define what makes these
+surveillance systems "smart". These smart camera network systems have common goals when it comes creating more efficient surveillance applications. First, the issue 
+of network resource utilization is an issue all systems need to consider if those surveillance systems are to be scalable in crowded wireless deployment 
 scenarios. Then in almost every application considering power consumption of each node is very important if one is give an analysis of the systems 
-efficiency. If these systems are to be monitoring public spaces the smart camera networks need to be keeping the data recorded secure and also ensuring 
-that the data recorded is actually quality information that could be used by officials. \\
+efficiency. If these systems are to be monitoring public spaces the smart camera networks need to be keeping the data recorded secure and also
+ensuring that the data recorded is actually quality information that could be used by officials.
 
-%% Wireless Smart Camera Networks Taxonomy Divided into 3 sections
-%% 1 Bandwidth efficieny 2 power consumption 3 Quality of data
 \subsection{Bandwidth Efficiency}
-Video data is rich with useful information that other sensor source can’t provide, however video data quickly becomes very large in size as time goes on.
-Nodes competing for network connectivity while maintaining quality on live video feed can soon become a problem as the network grows or if other nodes
-not in the system share the connection. One way to combat this is by assuring the data recorded is useful and actually recording video data that can be
-used to do detection of events. A common technique is to use other non-image sensors to provide separate data that can be used to determine if the camera
-should record video at all.
+Video data is rich with useful information that other sensor sources can’t provide, however video data quickly becomes very large in size as time goes 
+on.Nodes competing for network connectivity while maintaining quality on live video feed can soon become a problem as the network grows or if other 
+nodes not in the system share the connection. One way to combat this is by assuring the data recorded is useful and actually recording video data that 
+can be used to do detection of events by doing in network processing ~\cite{Citric}.\\
+Taking advantage of multiple cameras is a very useful method to determine not only which node has the best view of the object, but also if the overlapping
+video footage can be combined to provide more useful data. Extensive research has been done on both bandwidth and energy efficiencies of wireless
+smart camera networks that make use of overlapping footage ~\cite{AccLatEnergy}.
 
 \subsection{Lowering Power Consumption}
-When discussing wireless sensor networks , power consumption is always brought up as a concern
-
-\-- Use comparision chart in survey paper to show power consumption comparisons of current smart camera platforms\\ \\
+When discussing wireless sensor networks , power consumption is always brought up as a concern in deployment and scalability. Smart camera networks are 
+no different, and many researchers have discussed methods to design nodes that consume less power. One such method would be to limit the amount of time 
+a camera needs to actually be powered on, and rely on more low power sensors to trigger a wake up. Using this sensor fusing technique allows the system
+to operate a different power consumption states . Such states must be carefully looked at and many researchers 
+consider every level of operation of each camera node ~\cite{AccLatEnergy}~\cite{EnergyCons}. Making Smart hardware choices, such at choosing low power communication
+options such as 802.15.4, can also have a large effect on how much power the system uses.
 
 \subsection{Quality of data recorded}
+Recording live high-resolution data all the time with no inference will soon become a thing of the past. Every second of video recorded counts when the 
+surveillance system scales to much larger deployments such as in smart cities~\cite{HuSIMS}. Doing local proccessing and decision making first can have 
+a huge change on the amount of data that actually needs to be transmitted and archived. Whether it is event detection or object identification, preventing 
+false alarms by checking the data locally can be very helpful. The research area of computer vision has grown at a very fast rate and only in the past few years
+are we seeing wireless surveillance systems adopt these sophisticated algorithms.
 
-\section{Processing the Video Data}
+\twocolumn[
+\section{Classifying Smart Wireless Surveillance Systems}
+\begin{center}
+\captionof{table}{A taxonomy of current research surveillance systems that use wireless smart cameras.}
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{| l | p{3cm} | l | p{3cm} | p{2cm} | p{3cm} | p{3cm} | l| p{3cm} |}
+    \hline
+    System & Energy Efficiency & Multimodal & Bandwidth Efficiency & Wireless & Video Analysis & System Software & Multicamera & Security \\ \hline
 
+    Citric & sleeping nodes, only wake on presence of objects & Audio & In-network image processing, small image size & 802.15.4 and Bluetooth
+     & . & Embedded Linux & Yes & Pre-processing of data at node \\ \hline
+
+    HuSIMS & . & . & .  & . & . & . & . & .  \\ \hline
+
+    OmniEye & . & . & .  & WiPort 802.11b/g & . & . & . & .  \\ \hline
+
+    Wi-FLIP & . & . & .  & . & . & . & . & .  \\ \hline
+
+    SensEye & . & . & .  & . & . & . & . & .  \\ \hline
+
+    DTN-Citric & . & . & .  & . & . & . & . & .  \\ \hline
+
+    Flexi-WVSNP & . & . & .  & . & . & . & . & .  \\ \hline
+
+    MeshEye & . & . & .  & . & . & . & . & .  \\ \hline
+
+\end{tabular}}
+\end{center}
+]
+
+\subsection{Energy Efficiency}
+\subsection{Sensor Fusion}
+\subsection{Network Load and Scalability}
+\subsection{Wireless Communication}
+\subsection{Computer Vision in Surveillance}
 By the computer vision side, we can see that the background subtraction is the most used method to detect moving objects with single cameras in a 
@@
 
-The Citric system one that resembles ~\cite{CS-MoG} by the steps that are used in the object detection.
-At first they make a comparison of computational efficiency relative to the complexity of compressing and uncompressing using JPEG and Compressed Sensing, resulting in a better performance of the CS  for uncompressing.
-After that they use frame differencing to do background subtraction and then track the objects and store their tracks.
-On the HuSIMS system they take one step further after tracking the objects, it is implemented an algorithm that is able to trigger alarms if something looks irregular.
-After doing the object tracking they are able to define regions, representing where the most common tracks pass by, and sinks, representing places where the objects usually appear or disappear from the scene.
-Having these two defined sections there is an algorithm capable of analyzing the image and verify, for example, if the objects of a certain type is following the expected region for its type, or if the object went from one sink to another.
-In a case where one of these predicted behaviors looks different, an alarm is triggered notifying that a problem could happened.
-A problem very common with single camera systems is the object occlusions that can occurs when an object cross by other moving or static objects.
-A good method for this case is shown in ~\cite{Occlusion}.
-After a background subtraction using the Approximate Median Filter to detect the objects, they are classified accordingly to the change of their shape through the time.
-It is used a Kalman filter to predict the position of the objects and then compare the current positions with the predicted ones through an algorithm that allows the system to classify the object as a single person or a group of people.
-The particular characteristic of this algorithm is the ability to track objects with complete occlusion for a long duration.
-Different implementations for security camera networks are emerging, each one with its characteristics, performance and advantages.
-By looking at all the implementations already said, we can say that a good system could be made by the union of all these methods, if performances wasn’t a constraint, because in most of them it is used the same base algorithm but with different securities and tracking objectives.
-Create an efficient system could mean a hybrid one.
+The Citric system one that resembles ~\cite{CS-MoG} by the steps that are used in the object detection. At first they make a comparison of
+computational efficiency relative to the complexity of compressing and uncompressing using JPEG and Compressed Sensing, resulting in a better
+performance of the CS  for uncompressing. After that they use frame differencing to do background subtraction and then track the objects and store
+their tracks. On the HuSIMS system they take one step further after tracking the objects, it is implemented an algorithm that is able to trigger alarms
+if something looks irregular. After doing the object tracking they are able to define regions, representing where the most common tracks pass by, and
+sinks, representing places where the objects usually appear or disappear from the scene. Having these two defined sections there is an algorithm
+capable of analyzing the image and verify, for example, if the objects of a certain type is following the expected region for its type, or if the
+object went from one sink to another. In a case where one of these predicted behaviors looks different, an alarm is triggered notifying that a problem
+could happened. \\ \\
+A problem very common with single camera systems is the object occlusions that can occurs when an object cross by other moving or static objects. A
+good method for this case is shown in ~\cite{Occlusion}. After a background subtraction using the Approximate Median Filter to detect the objects, they
+are classified accordingly to the change of their shape through the time. It is used a Kalman filter to predict the position of the objects and then 
+compare the current positions with the predicted ones through an algorithm that allows the system to classify the object as a single person or a group 
+of people. The particular characteristic of this algorithm is the ability to track objects with complete occlusion for a long duration.
+Different implementations for security camera networks are emerging, each one with its characteristics, performance and advantages. By looking at all 
+the implementations already said, we can say that a good system could be made by the union of all these methods, if performances wasn’t a constraint, 
+because in most of them it is used the same base algorithm but with different securities and tracking objectives. Create an efficient system could mean 
+a hybrid one.
+\subsection{Management Software}
+\subsection{Multi-camera Advantages}
+\subsection{Securing The Data}
 
-\section{Example Wireless Smart Camera Systems}
+\section{The SWEETcam Project}
+As a proof of concept we've designed our own wireless smart camera node to help improve safety on campus. we've made use of the very popular RaspberryPi for
+its powerful processing capabilities, low cost, and its capability to run Linux. Some components we found very useful to achieve our goals including the 
+Broadcom SOC(System On a Chip), 700 MHz ARM processor, and its very own GPU for video processing. With the system running Linux, it was very easy for us to
+make use of many computer vision libraries already developed for Linux systems.\\
+We developed using the newly released Raspberry Pi camera module, which has an available API in C language and is capable of capturing 1920x1080 resolution
+color images with 30 fps rate. For the image processing, we chose the Open Source Computer Vision Library (OpenCv). Our computer vision system is developed in 
+C++ for better integration between the OpenCV and the API.
+\subsection{Energy Harvesting}
+Researchers agree that one way to combat the problems of lifetime performance with battery powered wireless sensor nodes is by making use of energy-harvesting
+capabilities~\cite{EnergyHarvesting}. We plan on achieving this with our system by using current solar technologies to recharge the camera's local battery. 
+Doing this we hope our system will require much less maintanence and remove any requirements for node placement near power grids.
 
-\-- A comparison chart of software design features (computer vision, network
-	topologies, bandwidth/energy saving techniques, etc. )\\ \\
-\-- Going into more detail of possibly one of the examples shown above in
-	the taxonomy\\ \\
-\-- A comparison chart of different hardware components of their systems 
-	being used\\ \\
-\-- A discussion of both research and commercial designs\\ \\
-
-\section{Our Project}
-
-\subsection{Hardware}
- \-- Discuss breifly about the different components and why they were chosen \\
-
-\subsubsection{Why we chose Wifi \\}
-\subsubsection{Multimodal capabilities \\}
-
-\subsection{Software}
-\subsubsection{Image Processing}
+\subsection{Image Processing}
 \- Considering the constraints of the system in terms of price and hardware, it is used techniques of background subtraction to do the object detection.
-When started, the program keep taking pictures and process them using Mixture of Gaussian (MoG) method by Stauffer and Grimson.
-With the foreground in hands we find the contours and then a bounded box is applied following the contours' limit.
-To remove some noise and false detection a step is added to ignore objects of small size.
-The object classification is the most processor consumption  processes for most of the pedestrian detection systems, because it is used training techniques to classify the objects based on a previous stored database.
-In our case, to reduce the process we classify the objects by looking at their dimensions, they are classified as human if the height is two times bigger than the width we classify as a person.
-\\
+When started, the program keep taking pictures and process them using Mixture of Gaussian (MoG) method by Stauffer and Grimson. With the foreground in
+hands we find the contours and then a bounded box is applied following the contours' limit. To remove some noise and false detection a step is added to 
+ignore objects of small size. The object classification is the most processor consumption  processes for most of the pedestrian detection systems, 
+because it is used training techniques to classify the objects based on a previous stored database. In our case, to reduce the process we classify the 
+objects by looking at their dimensions, they are classified as human if the height is two times bigger than the width we classify as a person. \\
 \begin{figure}[h!]
@@
 \end{figure}	
-\- This light system can generate some false alarms, but in association with the whole system, and its sensors, it can be improved for a better performance.
-There are other more robust object detection methods that could be used, but we would have a very low fps rate.
-\\
-\- We developed using the Raspberry Pi camera module, which has already an API in C language and capable of capturing 1920x1080 resolution color images with 30 fps rate.
-For the image processing, we chose the Open Source Computer Vision Library (OpenCv).
-Our computer vision system is developed in C++ for better integration between the OpenCV and the API.\\
+\- This light system can generate some false alarms, but in association with the whole system, and its sensors, it can be improved for a better
+performance. There are other more robust object detection methods that could be used, but we would have a very low fps rate.
 
-\subsection{Future Goals}
+\subsection{Tracking Object Behavior}
+Researchers in the computer vision  field are now moving to not only detect objects and their movements, but to then infer a given behavior is being displayed.
+Looking for patterns in the way objects move will help us make better assumptions about what those objects are doing at a more generic level. Using this
+information we can do better event detection for specific occurrences and tag the video recorded accordingly. For example, video data that specifically states
+it is a recording of a person by a bike rack late in the evening is much more useful that video recorded of just a person.
 
-\section{Future Directions for Smart Wireless Camera Networks}
-\-- Discuss research that has been proposed in the area and that is just begining to be implemented or hasn't yet at all.\\
-
-\section{Lessons to take away}
+\section{Future Directions and Lessons to take away}
+\-- Discuss research that has been proposed in the area and that is just beginning to be implemented or hasn't yet at all.\\
 
 \-- just so it compiles here are the references to be used:
-~\cite{DSPcam}
 ~\cite{HuSIMS}
@@
 ~\cite{OmniEye}
-~\cite{ScoutNode}
+~\cite{DTNSmartCamera}
 ~\cite{SensEye}
 ~\cite{WiFLIP}
+~\cite{AccLatEnergy}
+~\cite{MeshEye}
+~\cite{EnergyCons}
+~\cite{Flexi-WVSNP}
 
@@
 \begin{IEEEbiographynophoto}{Kevin Abas}
-Biography text here.
+is a graduate student at Univeristy of California Santa Cruz. His research
+interests include wireless sensor networks, computer networking, and embedded
+systems. He recieved his BSc in computer engineering from University of
+California Santa Cruz. Contact him at kabas@soe.ucsc.edu.
 \end{IEEEbiographynophoto}
@@
 
+\begin{IEEEbiographynophoto}{Katia Obraczka}
+Biography text here.
+\end{IEEEbiographynophoto}
+
 \end{document}
@@
 %%------------------------------------------------------------------------
-
-% *** MATH PACKAGES ***
-%
-%\usepackage[cmex10]{amsmath}
-% A popular package from the American Mathematical Society that provides
-% many useful and powerful commands for dealing with mathematics. If using
-% it, be sure to load this package with the cmex10 option to ensure that
-% only type 1 fonts will utilized at all point sizes. Without this option,
-% it is possible that some math symbols, particularly those within
-% footnotes, will be rendered in bitmap form which will result in a
-% document that can not be IEEE Xplore compliant!
-%
-% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
-% thus preventing page breaks from occurring within multiline equations. Use:
-%\interdisplaylinepenalty=2500
-% after loading amsmath to restore such page breaks as IEEEtran.cls normally
-% does. amsmath.sty is already installed on most LaTeX systems. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/
-
-% An example of a floating figure using the graphicx package.
-% Note that \label must occur AFTER (or within) \caption.
-% For figures, \caption should occur after the \includegraphics.
-% Note that IEEEtran v1.7 and later has special internal code that
-% is designed to preserve the operation of \label within \caption
-% even when the captionsoff option is in effect. However, because
-% of issues like this, it may be the safest practice to put all your
-% \label just after \caption rather than within \caption{}.
-%
-% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
-% option should be used if it is desired that the figures are to be
-% displayed while in draft mode.
-%
-%\begin{figure}[!t]
-%\centering
-%\includegraphics[width=2.5in]{myfigure}
-% where an .eps filename suffix will be assumed under latex, 
-% and a .pdf suffix will be assumed for pdflatex; or what has been declared
-% via \DeclareGraphicsExtensions.
-%\caption{Simulation Results.}
-%\label{fig_sim}
-%\end{figure}
-
-% Note that IEEE typically puts floats only at the top, even when this
-% results in a large percentage of a column being occupied by floats.
-
-% An example of a double column floating figure using two subfigures.
-% (The subfig.sty package must be loaded for this to work.)
-% The subfigure \label commands are set within each subfloat command,
-% and the \label for the overall figure must come after \caption.
-% \hfil is used as a separator to get equal spacing.
-% Watch out that the combined width of all the subfigures on a 
-% line do not exceed the text width or a line break will occur.
-%
-%\begin{figure*}[!t]
-%\centering
-%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
-%\label{fig_first_case}}
-%\hfil
-%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
-%\label{fig_second_case}}
-%\caption{Simulation results.}
-%\label{fig_sim}
-%\end{figure*}
-%
-% Note that often IEEE papers with subfigures do not employ subfigure
-% captions (using the optional argument to \subfloat[]), but instead will
-% reference/describe all of them (a), (b), etc., within the main caption.
-
-% An example of a floating table. Note that, for IEEE style tables, the 
-% \caption command should come BEFORE the table. Table text will default to
-% \footnotesize as IEEE normally uses this smaller font for tables.
-% The \label must come after \caption as always.
-%
-%\begin{table}[!t]
-%% increase table row spacing, adjust to taste
-%\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-%\caption{An Example of a Table}
-%\label{table_example}
-%\centering
-%% Some packages, such as MDW tools, offer better commands for making tables
-%% than the plain LaTeX2e tabular which is used here.
-%\begin{tabular}{|c||c|}
-%\hline
-%One & Two\\
-%\hline
-%Three & Four\\
-%\hline
-%\end{tabular}
-%\end{table}
-
-% Note that IEEE does not put floats in the very first column - or typically
-% anywhere on the first page for that matter. Also, in-text middle ("here")
-% positioning is not used. Most IEEE journals use top floats exclusively.
-% Note that, LaTeX2e, unlike IEEE journals, places footnotes above bottom
-% floats. This can be corrected via the \fnbelowfloat command of the
-% stfloats package.
-
-% if have a single appendix:
-%\appendix[Proof of the Zonklar Equations]
-% or
-%\appendix  % for no appendix heading
-% do not use \section anymore after \appendix, only \section*
-% is possibly needed
-
-% use appendices with more than one appendix
-% then use \section to start each appendix
-% you must declare a \section before using any
-% \subsection or using \label (\appendices by itself
-% starts a section numbered zero.)
-%

### 2013-10-31 Paper/main.tex
more of the table is done

@@
 \usepackage{caption}
+
+% ** UNIT PACKAGE  **
+\usepackage{siunitx}
+\sisetup{math-micro=\text{µ},text-micro=µ}
 %%----------------------------------------------------------------------
@@
 
-\title{Efficient Smart Camera Networks For Public Safety}
+\title{Smart Camera Networks For Public Safety}
 
@@
 Recording live high-resolution data all the time with no inference will soon become a thing of the past. Every second of video recorded counts when the 
-surveillance system scales to much larger deployments such as in smart cities~\cite{HuSIMS}. Doing local proccessing and decision making first can have 
+surveillance system scales to much larger deployments such as in smart cities~\cite{HuSIMS}. Doing local processing and decision making first can have 
 a huge change on the amount of data that actually needs to be transmitted and archived. Whether it is event detection or object identification, preventing 
@@
 \resizebox{\textwidth}{!}{%
-\begin{tabular}{| l | p{3cm} | l | p{3cm} | p{2cm} | p{3cm} | p{3cm} | l| p{3cm} |}
+\begin{tabular}{| l | p{4cm} | p{2cm}  | p{3cm} | p{2cm} | p{3cm} | p{3cm} | l| p{3cm} |}
     \hline
-    System & Energy Efficiency & Multimodal & Bandwidth Efficiency & Wireless & Video Analysis & System Software & Multicamera & Security \\ \hline
+    System & Energy Efficiency & Multimodal & Bandwidth Efficiency & Wireless & Video Analysis & System Software & Multicamera Overlap & Security \\ \hline
 
-    Citric & sleeping nodes, only wake on presence of objects & Audio & In-network image processing, small image size & 802.15.4 and Bluetooth
-     & . & Embedded Linux & Yes & Pre-processing of data at node \\ \hline
+    Citric & sleeping nodes, only wake on presence of objects & Audio & In-network image processing, small image size & 802.15.4
+     	& . & Embedded Linux & Yes & Pre-processing of data at node, wireless protocols \\ \hline
 
-    HuSIMS & . & . & .  & . & . & . & . & .  \\ \hline
+    HuSIMS & small processing power cameras, power efficient sensors & Smoke detectors, motion, light, humidity, Temperature 
+    & In-network image processing, Sink nodes, seperate low bandwidth sensor networks  
+    & WiMAX 4G & . & Large Management Software using semantic processing & No & given by 4g and secured at control center  \\ \hline
 
-    OmniEye & . & . & .  & WiPort 802.11b/g & . & . & . & .  \\ \hline
+    OmniEye & none described for cameras, seperate energy efficient sensor network & temperature light, sound sensors 
+    	& In-network image processing, data annotation 
+    	& 	WiPort 802.11b/g TSAM MAC & . & \textit{u}Linux & Yes & Data encrypted using PICO, SSL communication  \\ \hline
 
-    Wi-FLIP & . & . & .  & . & . & . & . & .  \\ \hline
+    Wi-FLIP & analog circuitry, low-level image processing, smart image processor & Light & Small images, Low framerate  
+    	& 802.15.4 & . & TinyOS & No & none described  \\ \hline
 
-    SensEye & . & . & .  & . & . & . & . & .  \\ \hline
+    SensEye & multi-tier cameras, cameras sleep because of redundant coverage  & none & low-latency wakeups and detection  
+    	& 802.11,  900MHz  & . & Embedded Linux & Yes & wireless protocols  \\ \hline
 
-    DTN-Citric & . & . & .  & . & . & . & . & .  \\ \hline
+    DTN-Citric & sleeping nodes, only wake on presence of objects & Audio & Distributed In-network processing, In-network storage  & 802.15.4 & . 
+    	& Embedded Linux  & Yes & Encrypted network traffic  \\ \hline
 
-    Flexi-WVSNP & . & . & .  & . & . & . & . & .  \\ \hline
+    Flexi-WVSNP & . & . & .  & 802.11, 802.15.4 & . & . & . & .  \\ \hline
 
@@
 \subsection{Energy Efficiency}
+All of the systems listed in Table 1 make an effort to reduce power consumption their system in some way. Getting the system to go into a low powered 
+sleep state during idle periods is a very effective solution ~\cite{AccLatEnergy} ~\cite{Citric}. Non-image sensors are already extremely energy efficient, 
+there for its often useful to use them to determine when the system should turn on the power hungry camera nodes. The image sensor itself can be design with
+analog circuitry and be more compact which will also reduce energy consumption~\cite{WiFLIP}. However the lower power consumption comes at a cost, and with
+the Wi-FLIP camera platform its frame rate.In surveillance systems with redundant coverage, which we discuss later, camera nodes can also tell their neighbor
+nodes to turn on or off based on the tracked object's trajectory in the scene~\cite{SensEye}.
+
 \subsection{Sensor Fusion}
+Using multiple sensors can also allow you to create more specific alarms cases that tell you more than just that an event occurred. The Human Situation
+Monitoring System does this on a very large scale by using numerous sensors is dense city deployments ~\cite{HuSIMS}. Sensors may be on the wireless camera
+node on may be on its own sensor network as in the OmniEye system ~\cite{OmniEye}. The extra sensors don't necessarily need to be non-image sensor but 
+could in fact be low powered camera sensors for simpler sensing tasks that then trigger larger more powerful cameras to be activated~\cite{SensEye}.
+
 \subsection{Network Load and Scalability}
+With high resolution streams coming from each of the camera nodes in these surveillance systems, it becomes impossible to have 
+that much video data be transmitted at once. Many systems take advantage of in-network processing before sending the data out to the internet or do processing on
+the wireless camera node itself ~\cite{HuSIMS}~\cite{OmniEye}. By annotating important data that displays and event of interest, system managers can request smaller sets 
+of data based on meta data~\cite{OmniEye}. Making use of sink nodes in densely populated sensor networks is also a very popular technique to reduce the 
+amount of rich video data needs to be sent over the internet~\cite{HuSIMS}.
+
 \subsection{Wireless Communication}
+If the surveillance system is densely populated and would cause to great a load on nearby networks, options such at WiMAX may be used ~\cite{HuSIMS}. 
+Researchers working on the OmniEye project have even design their own MAC layer protocols to scale better in larger topologies ~\cite{OmniEye}. In surveillance 
+situations where wireless communication is intermittent , delay tolerant networking techniques may be used ~\cite{DTNSmartCamera}. In DTN based systems, data
+may be allowed to accumulate locally before being transmitted securely over the internet.
+
 \subsection{Computer Vision in Surveillance}
@@
 a hybrid one.
+
 \subsection{Management Software}
+At the wireless camera  node level there are two clear options when it comes to operations systems, one either chooses an smaller architecture for 
+simplicity or one that can do on node processing and run more complicated analysis tools.
+It is well known that monitoring many feeds at once is very hard to automated and just does not scale well. Therefor some researchers are using semantic
+interpretation to abstract the raw data into more generic anomalies ~\cite{HuSIMS}.
+
 \subsection{Multi-camera Advantages}
+The Citric platform is not the only system that when deployed makes use of overlapping video data. Doing this allows the system to determine which angle 
+to best view the object or in what direction is the object heading.
+
 \subsection{Securing The Data}
+Privacy is a major concern is the design process of today's wireless sensor networks. Systems need to secure the private data that has been processed, the
+transmission link, and to location at which the data is stored. Many systems choose to rely on the standard methods provided by the technologies they use
+~\cite{HuSIMS}. While others make use of sophisticated encryption tools to secure its data and more commonly known secure communication tools such as Secure
+Socket Layer(SSL) ~\cite{OmniEye}. Wireless Surveillance systems must protect any data that could leak private information about objects and environments they track to those
+sniffing the communication medium.
 
@@
 C++ for better integration between the OpenCV and the API.
+
 \subsection{Energy Harvesting}
@@
 \-- Discuss research that has been proposed in the area and that is just beginning to be implemented or hasn't yet at all.\\
+\-- say that embedded systems are becoming more numerous and many of these techniques can be applied to those systems.
 

### 2013-11-10 Paper/main.tex
Finished Draft, unedited

@@
 %%
-%% Draft version 2.0
+%% Draft version 3.0
 %%
@@
 
+\usepackage{wrapfig}
+
 % ** UNIT PACKAGE  **
@@
 \begin{IEEEkeywords}
-Wireless sensor networks, Smart camera networks, Computer vision, Sensor networks, Human safety
+Wireless sensor networks, Smart camera networks, Computer vision, Image processing software, Human safety
 \end{IEEEkeywords}}
@@
 
-\IEEEPARstart{T}{his} paper discusses an overview of how Smart Camera Networks are changing surveillance systems of today.\\
-\-- Goals of the paper, What problems this papers solves, background, motivation \\
-\-- discuss Wireless sensor networks in general and how data rich video sensor are\\
-\-- Some things current Smart Camera networks assist with when it comes to 
-surveillance and crime detection nodes. \\
+\IEEEPARstart{W}{ireless} sensor networks are ushering in a new era of technologies that allow us to better interpret what is happening around us in urban and non-urban
+environments. Sensor data gives us better analysis about environmental trends, and could be used to effectively protect us from danger or monitor systems to make sure they
+remain in working order. With the help of these embedded sensing networks the dangers and problems of today will soon become a thing of the past thanks to research efforts.\\
+
+Video sensing networks provide the richest of data sets in comparison to other sensing technologies and therefor the number of applications for VSNs are increasing every day.
+With the right analysis tools a lot of information can be extracted from video data and researchers have come very far in designing camera platforms for this task. How efficient
+these systems are is very important, especially when the number of video sensors grow large as is required in surveillance applications.\\
 
@@
 
+\begin{figure*}
+\centering
+\includegraphics[scale=0.3]{CameraDepolymentsFigure.png}
+\caption{\textbf{(A)} Shows a multi-tier smart camera network in which more efficient low cost camera do object detection and wake up higher resolution cameras to run computer
+vision algorithms. \textbf{(B)} Is an example of sensor fusion where non-image sensing networks can use its data with the video data to make a better evaluation of the situation.
+\textbf{(C)} An object being detected by redundant coverage can be given a position in three dimensional space for computer vision algorithms to use.}
+\end{figure*}
+
 \section{Wireless Smart Camera Surveillance}
 Researchers and Commercial companies are designing wireless smart camera networks in surveillance applications to prevent crimes, detect environmental emergencies,
-monitor behavior of the elderly, and track vehicular traffic in public spaces. Many camera platforms have been designed to meet strict hardware requirements
-~\cite{Flexi-WVSNP} for wireless deployment in surveillance systems. However, different requirements must be stated when looking at the application specific 
+monitor behavior of the elderly, and track vehicular traffic in public spaces.
+Many camera platforms have been designed to meet strict hardware requirements~\cite{Flexi-WVSNP}~\cite{Citric}~\cite{WiFLIP} for wireless deployment in surveillance systems.
+However, different requirements must be stated when looking at the application specific
 scenario of surveillance in public spaces. To understand how these state of the art systems are improving on designs of the past, one must define what makes these
@@
 can be used to do detection of events by doing in network processing ~\cite{Citric}.\\
+
 Taking advantage of multiple cameras is a very useful method to determine not only which node has the best view of the object, but also if the overlapping
@@
 \subsection{Quality of data recorded}
+Vision sensor data requires much higher bandwidth due to its two-dimensional nature of its pixel arrays, and such data can not be fully analyzed by humans~\cite{MeshEye}.
 Recording live high-resolution data all the time with no inference will soon become a thing of the past. Every second of video recorded counts when the 
@@
 
-\twocolumn[
-\section{Classifying Smart Wireless Surveillance Systems}
-\begin{center}
-\captionof{table}{A taxonomy of current research surveillance systems that use wireless smart cameras.}
-\resizebox{\textwidth}{!}{%
-\begin{tabular}{| l | p{4cm} | p{2cm}  | p{3cm} | p{2cm} | p{3cm} | p{3cm} | l| p{3cm} |}
+\section{Smart Camera Advantages}
+
+Researchers are using common design strategies to overcome chalanges when using smart camera networks for surveillance. From deployment strategies to choosing efficient
+hardware and software, researchers are making wireless surveillance systems smarter. Before presenting our taxonomy of current research systems, we will define
+some terminology and present some generic concepts.
+
+\subsection{Efficiency in Smart Camera Networks}
+Measuring performance in a wireless smart camera networks can be broken up into 2 specific categories. One having to do when environmental impact of these systems its important
+to measure how much energy these monitoring systems use on a daily basis. Many strategies from other wireless sensor networks can be used in this scenario including
+making use of nodes that sleep during idle times. Another technique is to use hardware that uses less power to decide if it needs to wake the more power hungry video sensors.
+
+A few solutions to both performance concerns show up in many systems design by researchers today. As shown in Figure 1, smaller more energy and bandwidth efficient sensor networks
+could provide smaller meta data such and audio and temperature data to complement what the video sensor captures. When Computers analyze both data sets and
+make an inference about them its called sensor fusion or multi-modal sensor networks. Designing the vision sensor network to take advantage of two classes of cameras, one 
+efficient and the other more powerful and higher resolution, also helps with performance. Deciding on a smart deployment strategy can also be very beneficial,
+especially in scenarios with overlapping coverage. Getting multiple views of an object get give more data and much more accuracies.
+
+\subsection{Implementation strategies}
+An important decision made when designing smart camera platforms is what communication medium will be chosen. Many systems choose Zigbee(802.15.4) as their wireless 
+communication link for its low power features, whereas if your system has a higher bandwidth requirement researchers choose the more ubiquitous WiFi(802.11). The camera platforms
+and monitoring systems software architecture must also be analyzed when classifying effectiveness in the application of surveillance. Classifying the systems security mechanism 
+to both secure the data and also its transmission channels.
+
+\subsection{Common Computer Vision Techniques}
+
+\subsubsection{Object Detection and Recognition}
+One the objectives of the computer vision and the image processing, is the ability of identify and classify instances of real-world objects in images or videos.
+It has been developed different algorithms with different approaches to this same problem. There are 2 main used techniques for object detection, one based on 
+training the objects to be detected and recognized, while the other is based on detecting moving objects using background subtraction and recognize 
+them through the shape.
+
+\subsubsection{Behavior Tracking}
+An area is emerging in the surveillance systems, algorithms capable of tracking the human behaviour to better categorize the data being recorded. The use of 
+this kind of system can automate the process of analysing the human movements and, from there, identify abnormal behaviors and hostile intent  that can be 
+translated as alerts for the system supervisors.
+
+\subsubsection{Occlusion Handle}
+Surveillance cameras are usually developed to work independent of the ambient. Therefore, scenarios that have many obstacles that can occlude the vision of 
+the camera over the detected object can represent a problem. In order to increase the tracking capability of the systems, some of them have an additional 
+component responsible for the occlusion handle, in other words, the system is able to track the object even if it cross by another moving or static object.
+
+\begin{table*}[t]
+  \centering
+
+  \begin{tabular}{| p{1.1cm} | p{2cm} | p{1.2cm}  | p{2.1cm} | p{1cm} | p{2.5cm} | p{1.5cm} | p{1.3cm}  | p{2cm} |}
     \hline
@@
     Citric & sleeping nodes, only wake on presence of objects & Audio & In-network image processing, small image size & 802.15.4
-     	& . & Embedded Linux & Yes & Pre-processing of data at node, wireless protocols \\ \hline
+     	& \textbf{Compression:} Compressed Sensing, \textbf{Object Detection:} Frame Differencing Background Subtraction, \textbf{OcclusionHandle:} Multiple Cameras For One Object 
+        & Embedded Linux & Yes & Pre-processing of data at node, wireless protocols \\ \hline
 
     HuSIMS & small processing power cameras, power efficient sensors & Smoke detectors, motion, light, humidity, Temperature 
-    & In-network image processing, Sink nodes, seperate low bandwidth sensor networks  
-    & WiMAX 4G & . & Large Management Software using semantic processing & No & given by 4g and secured at control center  \\ \hline
+    	& In-network image processing, Sink nodes, separate low bandwidth sensor networks  
+    	& WiMAX 4G & \textbf{Alerts:} Object Abnormal Behavior & Large Management Software using semantic processing 
+    	& No & given by 4g and secured at control center  \\ \hline
 
@@
     	& In-network image processing, data annotation 
-    	& 	WiPort 802.11b/g TSAM MAC & . & \textit{u}Linux & Yes & Data encrypted using PICO, SSL communication  \\ \hline
+    	& 	WiPort 802.11b/g TSAM MAC & \textbf{Compression:} JPEG 70\% ,   \textbf{Object Detection:} Adaptive Background Subtraction 
+        & \textit{u}Linux & Yes & Data encrypted using PICO, SSL communication  \\ \hline
 
     Wi-FLIP & analog circuitry, low-level image processing, smart image processor & Light & Small images, Low framerate  
-    	& 802.15.4 & . & TinyOS & No & none described  \\ \hline
+    	& 802.15.4 & \textbf{Object Detection:} Difference of Gaussians  & TinyOS & No & none described  \\ \hline
 
     SensEye & multi-tier cameras, cameras sleep because of redundant coverage  & none & low-latency wakeups and detection  
-    	& 802.11,  900MHz  & . & Embedded Linux & Yes & wireless protocols  \\ \hline
+    	& 802.11,  900MHz  & \textbf{Object Detection:} Frame Differencing Background Subtraction, \textbf{OcclusionHandle:} Multiple Cameras For One Object  
+        & Embedded Linux & Yes & wireless protocols  \\ \hline
 
-    DTN-Citric & sleeping nodes, only wake on presence of objects & Audio & Distributed In-network processing, In-network storage  & 802.15.4 & . 
-    	& Embedded Linux  & Yes & Encrypted network traffic  \\ \hline
+    DTN-Citric & sleeping nodes, only wake on presence of objects & Audio & Distributed In-network processing, In-network storage  & 802.15.4 
+    	& \textbf{Object Detection:} Not Specified Background Subtraction & Embedded Linux  & Yes & Encrypted network traffic  \\ \hline
 
-    Flexi-WVSNP & . & . & .  & 802.11, 802.15.4 & . & . & . & .  \\ \hline
+    Flexi-WVSNP & switching between radios, efficient SoC processor & Zigbee sensor network  & switching between radio's to control channel utilization  
+    	& 802.11, 802.15.4 & None Described & Custom SoC Firmware & No & None described  \\ \hline
 
-    MeshEye & . & . & .  & . & . & . & . & .  \\ \hline
+    MeshEye & Low powered transievers, designed for battery power & none & Distributed in-network processing   & 802.15.4 
+    	& \textbf{Object Detection:} Frame Differencing Background Subtraction & Custom Arm7 microcontroller firmware & No & None Described  \\ \hline
 
-\end{tabular}}
-\end{center}
-]
+  \end{tabular}
+  \caption{}{A taxonomy of current research surveillance systems that use wireless smart cameras}
+  \label{tab:1}
+\end{table*}
+
+\section{Classifying Smart Wireless Surveillance Systems}
 
@@
 the Wi-FLIP camera platform its frame rate.In surveillance systems with redundant coverage, which we discuss later, camera nodes can also tell their neighbor
-nodes to turn on or off based on the tracked object's trajectory in the scene~\cite{SensEye}.
+nodes to turn on or off based on the tracked object's trajectory in the scene~\cite{SensEye}.Efficient SoC processor are now more advance and can handle
+managing a smart camera node while being energy efficient~\cite{Flexi-WVSNP}.
 
@@
 of data based on meta data~\cite{OmniEye}. Making use of sink nodes in densely populated sensor networks is also a very popular technique to reduce the 
-amount of rich video data needs to be sent over the internet~\cite{HuSIMS}.
+amount of rich video data needs to be sent over the internet~\cite{HuSIMS}. Another important factor to consider when discussing network load is channel utilization,
+minimizing time spent on one wireless communication by sending data on another also helps in network load efficiences~\cite{Flexi-WVSNP}.
 
@@
 If the surveillance system is densely populated and would cause to great a load on nearby networks, options such at WiMAX may be used ~\cite{HuSIMS}. 
-Researchers working on the OmniEye project have even design their own MAC layer protocols to scale better in larger topologies ~\cite{OmniEye}. In surveillance 
+Researchers working on the OmniEye project and MeshEye project have even design their own MAC layer protocols to scale better in larger topologies ~\cite{MeshEye}~\cite{OmniEye}. In surveillance 
 situations where wireless communication is intermittent , delay tolerant networking techniques may be used ~\cite{DTNSmartCamera}. In DTN based systems, data
-may be allowed to accumulate locally before being transmitted securely over the internet.
+may be allowed to accumulate locally before being transmitted securely over the internet. Systems may have a hybrid communication system, where they take advantage of
+two seperate radios~\cite{Flexi-WVSNP}. Doing this could reduce the amount of traffic produced by the node to any of the 2 radio communication links.
 
 \subsection{Computer Vision in Surveillance}
-By the computer vision side, we can see that the background subtraction is the most used method to detect moving objects with single cameras in a 
-real-time world. There are different algorithms to implement it, with different computer efficiencies and accuracies, what can make each one more
-suitable for each system. Methods like Mixture of Gaussians (MoG) or simple frame differencing are largely used, but the problem with these methods is
-their computational efficiency. In ~\cite{CS-MoG} it is shown the possibility of having a low power and computationally efficient (up to 5 times
-faster) system based on background subtraction using a known method: Compressed Sensing. Using CS is possible to compress the image, in other words,
-reduce the amount of data to be processed, while retaining much of the original image. The compressed image can be submitted to a MoG algorithm to
-detect the objects on the scene with a lower solution complexity. The results shown a very efficient system, that they called CS-MoG, with an accuracy
-very close to a system that uses MoG only.
+As already said, it would be very helpful if all the captured images could be analysed in the node before being uploaded and saved. Most of the systems that use in node
+data process are using background subtraction method to detect moving objects with single cameras in real-time. There are different algorithms to implement it, with 
+different computer efficiencies and accuracies, what can make each one more suitable for each system.
 
-The Citric system one that resembles ~\cite{CS-MoG} by the steps that are used in the object detection. At first they make a comparison of
-computational efficiency relative to the complexity of compressing and uncompressing using JPEG and Compressed Sensing, resulting in a better
-performance of the CS  for uncompressing. After that they use frame differencing to do background subtraction and then track the objects and store
-their tracks. On the HuSIMS system they take one step further after tracking the objects, it is implemented an algorithm that is able to trigger alarms
-if something looks irregular. After doing the object tracking they are able to define regions, representing where the most common tracks pass by, and
-sinks, representing places where the objects usually appear or disappear from the scene. Having these two defined sections there is an algorithm
-capable of analyzing the image and verify, for example, if the objects of a certain type is following the expected region for its type, or if the
-object went from one sink to another. In a case where one of these predicted behaviors looks different, an alarm is triggered notifying that a problem
-could happened. \\ \\
-A problem very common with single camera systems is the object occlusions that can occurs when an object cross by other moving or static objects. A
-good method for this case is shown in ~\cite{Occlusion}. After a background subtraction using the Approximate Median Filter to detect the objects, they
-are classified accordingly to the change of their shape through the time. It is used a Kalman filter to predict the position of the objects and then 
-compare the current positions with the predicted ones through an algorithm that allows the system to classify the object as a single person or a group 
-of people. The particular characteristic of this algorithm is the ability to track objects with complete occlusion for a long duration.
-Different implementations for security camera networks are emerging, each one with its characteristics, performance and advantages. By looking at all 
-the implementations already said, we can say that a good system could be made by the union of all these methods, if performances wasn’t a constraint, 
-because in most of them it is used the same base algorithm but with different securities and tracking objectives. Create an efficient system could mean 
-a hybrid one.
+\subsubsection{Object Detection and Recognition}
+Methods like Mixture of Gaussians (MoG) ~\cite{CS-MoG} or frame differencing, sometimes with adaptive background, are largely used ~\cite{OmniEye}~\cite{SensEye}~\cite{MeshEye}, but 
+the computational efficiency still a problem. In Johnsen and Tews ~\cite{Occlusion}. it is shown the possibility of having a low power and computationally efficient 
+(up to 5 times faster) system based on  background subtraction using a very known method: Compressed Sensing. Using CS is possible to compress the image, in other words, reduce 
+the amount of data to be processed, while retaining much of the original image. The compressed image can be submitted to a MoG algorithm to detect the objects on the scene with 
+a lower solution complexity. The results shown a very efficient system, that they called CS-MoG, with an accuracy very close to a system that uses MoG only.
+
+The CITRIC ~\cite{Citric} system resembles Johnsen and Tews ~\cite{Occlusion}. by the steps that are used in the object detection. At first they use CS to compress the image, 
+then they use frame differencing to do background subtraction and apply Canny edge detection algorithm to detect the objects. On their most recent work, they describe a new 
+method called Distributed Object Recognition, where they try to boost the recognition accuracy using multiple cameras to recognize the same object. Motivated by the CS and its
+applications in sensor networks, they show that the visual histogram of the features that describe an object in a single image is spare, and most of its coefficients are positive
+and approximately zero. Furthermore, since SIFT-type features (e.g., SIFT [Lowe 1999], SURF [Bay et al. 2008], or CHoG [Chandrasekhar et al. 2009]) are robust to some degree of 
+camera rotation and translation, it is possible to relate the non zero coefficients of the features from one camera with the others from other cameras. This phenomenon is called 
+joint sparsity (JS).
+
+\subsubsection{Behavior Tracking}
+On the HuSIMS system ~\cite{HuSIMS} they take one step further after tracking the objects, it is implemented an algorithm that is able to trigger alarms if something looks
+irregular. Afterdoing the object tracking they are able to define regions, representing where the most common tracks pass by, and sinks, representing places where the objects
+usually appear or disappear from the scene. Having these 2 defined sections there is an algorithm capable of analysing the image and verify, for example, if the objects of a
+certain type is following the expected region for its type, or if the object went from one sink to another. In a case where one of these predicted behaviours looks different,
+an alarm is triggered notifying that a problem could happened.
+
+\subsubsection{Occlusion Handle}
+A problem very common with single camera systems is the object occlusions. A good method for this case is presented in [8 check]. After a background subtraction they are 
+classified accordingly to the change of their shape through the time. It is used a Kalman filter to predict the position of the objects and then compare the current position
+with the predicted one through an algorithm that allows the system to even distinguish between a single person or a group of people as seen on Figure 2 The particular 
+characteristic of this algorithm is the ability to track objects with complete occlusion for a long duration.
+
+\begin{figure}[h!]
+\centering
+\includegraphics[scale=0.5]{Occlusion.png}
+\caption{Occlusion handle algorithm as described by Swantje Johnsen and Ashley Tews ~\cite{Occlusion}.}
+\end{figure}
+
+Others occlusion handle methods can be used. On HuSIMS  ~\cite{HuSIMS} , a less accurate, but also less complex, detects the edges along which a target disappears and then fits
+lines. Another example is CITRIC ~\cite{Citric}, where they take the advantage of multiple cameras and the distributed recognition to keep the track of an object even after 
+the object become occluded for one of the cameras.
 
@@
 
-\subsection{Multi-camera Advantages}
-The Citric platform is not the only system that when deployed makes use of overlapping video data. Doing this allows the system to determine which angle 
-to best view the object or in what direction is the object heading.
+\subsection{Overlapping Multi-camera Advantages}
+The Citric project designed their camera node to incorporate redundant coverage into their video analysis, and can track and object in 3 dimensional space if the object
+is found in the view of two cameras~\cite{OmniEye}~\cite{DTNSmartCamera}.The Citric platform is not the only system that when deployed makes use of overlapping video data. 
+Not only are the cameras over lapping in the SensEye system, but their two levels of complexity because of their multi-tiered camera setup~\cite{SensEye}.
 
@@
 C++ for better integration between the OpenCV and the API.
+
+\subsection{Project overview}
+
+\-- show both software and hardware diagram
 
@@
 \section{Future Directions and Lessons to take away}
-\-- Discuss research that has been proposed in the area and that is just beginning to be implemented or hasn't yet at all.\\
-\-- say that embedded systems are becoming more numerous and many of these techniques can be applied to those systems.
-
-\-- just so it compiles here are the references to be used:
-~\cite{HuSIMS}
-~\cite{Citric}
-~\cite{OmniEye}
-~\cite{DTNSmartCamera}
-~\cite{SensEye}
-~\cite{WiFLIP}
-~\cite{AccLatEnergy}
-~\cite{MeshEye}
-~\cite{EnergyCons}
-~\cite{Flexi-WVSNP}
+Many Embedded systems can apply the same classification we present here to their systems as well. Such systems become more numerous every day and therefor their
+footprint on both the amount of energy they consume and the load they add to today's Internet is important. For such architectures to remain scalable,
+future monitoring system will need to be more self reliant which includes having decision making and data processing be done from within the system itself.
+Much research still remains to achieve this goal in smart camera networks for surveillance and other sensor networks and systems.
 
